\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{ragged2e}  % Add this line to enable \justify
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Muhammad Khalil Ashraf} \\ \vspace{1pt}
    \small +923098627770 $|$ \href{mailto:khalilashraf28@gmail.com}{\underline{khalilashraf28@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/muhammad-khalil-ashraf-95061a270/}{\underline{linkedin.com/in/muhammad-khalil-ashraf}} $|$
    \href{https://github.com/khalilashraf28}{\underline{github.com/khalilashraf28}}
\end{center}

%-----------SUMMARY-----------
\section{SUMMARY}
\justify
Driven data enthusiast with a background in Computer Engineering, currently an undergraduate specializing in data science and machine learning. Highly proficient in Exploratory Data Analysis (EDA), Data Science methodologies, SQL and Machine Learning (ML),. Hands-on experience gained through industry internships, continuously refining skills through independent data-driven projects. Equipped to excel in digital intelligence environments, leveraging cutting-edge machine learning techniques and staying at the forefront of technological advancements. Passionate about solving complex data challenges, with a relentless drive to master new tools and methodologies in data science and data management.

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Sir Syed University of Engineering and Technology}{Karachi, Pakistan}
      {Bachelor of Science in Computer Engineering}{ Oct 2021 -- Present}
    \resumeSubheading
      {Jinnah Government College}{Karachi, Pakistan}
      {Pre-Engineering}{Aug. 2019 -- Aug 2021}
    \resumeSubheading
      {As-suffah Madina-tul Ilm Academy}{Karachi, Pakistan}
      {Science}{Jan. 2011 -- July 2019}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Artificial Intelligence Intern}{Oct 2024 -- Present}
      {Xclusive Trading Inc.}{}
     \resumeItemListStart
      \resumeItem{Designed and implemented an advanced Multi-Camera Customer and Employee Tracking and Re-Identification (ReID) System for over 230 Metro T-Mobile stores owned by XTI across the US, leveraging cutting-edge technologies to enhance operational efficiency.}
      \resumeItem{Analyzed multiple real-time camera streams to extract key performance metrics, delivering actionable insights that improved customer engagement, staff efficiency, and location security, including commission and chargeback data analysis.}
      \resumeItem{Designed and deployed an InfoBip chatbot to assist new Store Managers and Representatives, streamlining the onboarding process and improving access to information.}
      \resumeItem{Developed Streamlit dashboards for real-time data visualization and insights across the company, enabling data-driven decisions and optimizing overall operations, including performance, commission, goals, and attendance dashboards.}
      \resumeItem{Skills Gained: Enhanced expertise in computer vision, ReID, and Streamlit.}
    \resumeItemListEnd

    \resumeSubheading
      {Machine Learning Intern}{May 2024 -- June 2024}
      {CodexCue}{Remote}
      \resumeItemListStart
        \resumeItem{Collaborated on machine learning model development and implementation for real-world applications.}
        \resumeItem{Conducted data preprocessing and feature engineering to improve model accuracy.}
      \resumeItemListEnd

    \resumeSubheading
      {Data Science Intern}{September 2023 -- October 2023}
      {TechnoHacks}{Remote}
      \resumeItemListStart
        \resumeItem{Built predictive models and performed statistical analysis on large datasets.}
        \resumeItem{Automated data visualization processes to generate insights for stakeholders.}
      \resumeItemListEnd

    \resumeSubheading
      {Data Science Intern}{August 2023 -- September 2023}
      {CodSoft}{Remote}
      \resumeItemListStart
        \resumeItem{Applied different types of machine learning algorithms and techniques for analysis.}
        \resumeItem{Performed data preprocessing and developed insightful data visualizations to present findings.}
    \resumeItemListEnd

    \resumeSubheading
      {Front End Developer Intern}{August 2023 -- September 2023}
      {Interns Pakistan}{Remote}
      \resumeItemListStart
        \resumeItem{Designed and implemented responsive web interfaces using HTML, CSS, Bootstrap, and JavaScript.}
        \resumeItem{Optimized website performance and ensured cross-browser compatibility.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd




%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
        \textbf{Programming Languages}{: Python, Java, C++, MATLAB, SQL} \\
        \textbf{Machine Learning}{: Development of predictive models, Classification, Regression, and Clustering tasks} \\
        \textbf{Data Visualization}{: Matplotlib, Seaborn, ggplot2, Plotly} \\
        \textbf{Data Manipulation and Cleaning}{: Data cleaning, Data preprocessing, Feature engineering} \\
        \textbf{Deep Learning}{: TensorFlow, CNN} \\
        \textbf{Libraries}{: Pandas, NumPy, TensorFlow, Scikit-Learn} \\
        \textbf{Frameworks}{: Streamlit, BootStrap, Flask} \\
    }}
\end{itemize}


%-----------VOLUNTEERING/COMMUNITY SERVICES-----------
\section{Volunteering/Community Services}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
        \textbf{Chairperson}{ (IEEE-SSUET Computer Society)} \hfill October 2024 - Present \\
        \textbf{Core Team Member}{ (Google Developer Student Club - SSUET)} \hfill August 2023 - August 2024 \\
        \textbf{Marketing Team Lead}{ (Event: STEP-GEN'23 by IEEE Young Professionals, IEEE SSUET Student Branch)} \hfill STEP-GEN'23 
    }}
\end{itemize}

%-----------LICENSES AND CERTIFICATIONS-----------
\section{Licenses and Certifications}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
        \textbf{IBM Data Science Professional Certificate}{ (IBM)} \hfill Issued October 31, 2023 \\
        \textit{Link: \href{https://www.coursera.org/account/accomplishments/professional-cert/2MLAPSSJ96LS}{https://www.coursera.org/account/accomplishments/professional-cert/2MLAPSSJ96LS}} \\
        \textbf{Machine Learning}{ (DeepLearning.ai and Stanford University)} \hfill Issued August 27, 2023 \\
        \textit{Link: \href{https://www.coursera.org/account/accomplishments/specialization/9778UDG7CZS5}{https://www.coursera.org/account/accomplishments/specialization/9778UDG7CZS5}} \\
        \textbf{Artificial Intelligence}{ (National Vocational and Technical Training Commission NAVTTC)} \hfill Issued August 22, 2023 \\
        \textit{Link: \href{https://drive.google.com/file/d/1FSup__JP3Q3Ow9rN3iB2EWKxxT1_M6Dh/view?pli=1}{https://drive.google.com/file/d/1FSup__JP3Q3Ow9rN3iB2EWKxxT1_M6Dh/view?pli=1}} \\
        \textbf{Learn to Program: The Fundamentals}{ (University of Toronto)} \hfill Issued October 30, 2022 \\
        \textit{Link: \href{https://www.coursera.org/account/accomplishments/verify/8Q99GCQVDV9Z}{https://www.coursera.org/account/accomplishments/verify/8Q99GCQVDV9Z}} \\
        \textbf{Graphics Designer}{ (DigiSkills.pk)} \hfill Issued November 30, 2019 \\
        \textit{Link: \href{https://digiskills.pk/verify/}{https://digiskills.pk/verify/} (Certificate ID: JXQP3P3PQ)} 
    }}
\end{itemize}

\end{document}
